%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MSc. Computer Science (Distinction)} % Degree
    {Newcastle University} % Institution
    {Newcastle, England} % Location
    {September. 2016 - December. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Achieved a final average of \%78 raw marks.}
        \item {Awarded for best team project having played a leadership role as a team manager.}
      \end{cvitems}
    }

  \cventry
    {BA. Philosophy (2.2)} % Degree
    {University of Leeds} % Institution
    {Leeds, England} % Location
    {September. 2012 - July. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Flourished in programming electives with project focus on user accessibility.}
        \item {Provided expertise in qualitative analysis, critical evaluation, assessment, and technical writing as practised investigating philosophical concepts, in particular the philosophy of modern physics (general relativity).}
        \item {Provided expertise in explaining complex concepts (i.e. complex data structures) to be clearly communicated or well-understood towards individuals without detailed or technical knowledge about the subject (i.e. by abstracting, simplifying, or reducing the concept).}
        \item {Research experience in ethical evaluation and analysis, evaluation of scientific methodology, and systems of formal logic (i.e. propositional logic and Kripke semantics).}
      \end{cvitems}
    }

  \cventry
    {A-Levels} % Degree
    {Queen Elizabeth Sixth Form College} % Institution
    {Darlington, England} % Location
    {September. 2009 - August. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {History (A*), Philosophy (B), English Language (C).}
      \end{cvitems}
    }

  \cventry
    {GCSE's} % Degree
    {Hurworth Comprehensive School} % Institution
    {Hurworth, England} % Location
    {September. 2004 - August. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {English Literature (A*), Additional Science (A*), Physics (A*), Information and Technology (A*), English Language (A), Science (A), Biology (A), History (A), Chemistry (A), Mathematics (B), Geography (C), Statistics (C).}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
