%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Junior Software Developer} % Job title
    {RHEA Group} % Organization
    {Harwell Oxford, England} % Location
    {Feburary. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained a RESTful API written in Go working closely with data engineers and UI developers to facilitate the flow of data through an Apache NiFi, NoSQL database, Go API, and Django production solution stack. Translated user stories to end-user features. Provided documentation and development of relational databases, NoSQL databases, and graph databases, to help determine which best fits the project use case.}
        \item {Developed a GraphQL API within the Phoenix web framework (MVC), and a bespoke data-parsing tool to stream shapefile and GeoJSON data to databases in Elixir. Provisioned shell scripts for their deployment to Vagrant development environments and Amazon EC2 instances.}
      \end{cvitems}
    }

  \cventry
    {Support Consultant} % Job title
    {EMIS Health} % Organization
    {Leeds, England} % Location
    {December. 2015 - September. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Attained a first-class insight to technology development and deployment of clinical software systems which grounded my critical thinking, technical writing, and social and communication skills  (i.e. consultation and presentation) in an applied enterprise environment.}
	\item {Developed customer service skills through interfacing with clients, support, and development teams of accredited suppliers over the phone, to investigate API faults of third party software for the flagship application EMIS Web. This involved negotiating problem resolution strategies and technical writing to suit each of those stakeholders.}
	\item{Developed technical skills through investigating API faults for third party suppliers, interpreting C\# stack trace for fault resolution, peer-reviewing and querying T-SQL for estate-wide configuration and issue diagnosis, creating automation scripts for repetitive problem management (i.e. batch or Python), and problem handling network transmissions using in-house tools and Wireshark. Many resolutions I proposed were contributed to the support knowledge base.}
      \end{cvitems}
    }

  \cventry
    {Team Member} % Job title
    {Rockliffe Hall Hotel} % Organization
    {Hurworth, England} % Location
    {December. 2011 - March. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Social experience empathising with customer grievences for problem resolution.}
        \item{Using conversation skills to make customers feel continually welcome and ensure the business remained competitive and efficient.} 
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
