  \cventry
    {Locomotion Client.} % Job title
    {Group Project, Newcastle University} % Organization
    {permalink} % Location
    {December. 2016 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {For a mock railway service application (similar to 'trainline.com') I acted as group project team-leader, the focal point for group meetings and managing the development process. My key responsibilities included organising meetings, designing and modularizing the solution architecture, motivating feedback from team-members, escalating significant risk to the project as necessary, splitting the designed solution into manageable sets of objectives and milestones and ensuring they were met, problem management (supporting team members and troubleshooting their code in one-to-one sessions).
  \item {I was soley responsible for the research, design, and implementation of a unique fastest time routing algorithm for the mock railway service web-application, and presenting the implementation to examiners.}
  \item {Where a classical approach for modelling time-table information is a database of stations and trains stopping at each station, the designed implementation deviated from this approach by introducing a system of conjunctive train-time and station nodes the topology of which identified which connecting train-times and stations were reachable. Searches for fastest train times from A-B were then performable using a depth first search through connected nodes.}
  \item {The routing solution was finally implemented as a module in the overall project using an object-oriented architecture written in PHP.}
      \end{cvitems}
    }

      \cventry
    {Switch Configuration Client.} % Job title
    {Subcontract.} % Organization
    {None} % Location
    {December. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Delivered a network capable leveraged configuration management tool for deployment of a large number of stacked switches containing
mixed switch models, requiring a degree of flexible options to create the appropriate stack mix.}
      \end{cvitems}
    }

    {Tournament Client.} % Job title
    {Personal Project.} % Organization
    {None} % Location
    {December. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Developed a “matchmaking application” using a written algorithm to arrange a database of users based on all users ranked relative to each other and from this organize those users into manageable sets of the same average rank, so apt to compete against each other in an online video game tournament. Hosted that tournament on a Ubuntu server then broadcast to the larger involved community.}
      \end{cvitems}
    }